Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
piccole modifiche

The proposed tampering-detection algorithm analyzes a sequence of frames $\{z_t\}_t$ to detect the time instant $\tau^*$ when tampering like \eqref{eq:model_defocus} or \eqref{eq:model_displacement} occurs. We assume that $T_0$ tampering-free frames are provided for training.

@@

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consist in computing of the indicators, in particular $g$. Computing $g$ requires, when using the Sobel filters in~\eqref{eq:normaGradiente}, $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}, while computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively. Detecting outliers in the indicators requires two comparisons per frame: thus, monitoring regions instead of the whole image has a negligible impact on the overall computational complexity. Algorithm~\ref{alg:DISPL} has very low memory requirements: $l$ and $g$ indicators can be computed online, while $d$ requires to store a single frame in memory. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of separately monitoring regions in a tampering-detection framework like Algorithm~\ref{alg:DISPL}. To this purpose, we show that Algorithm~\ref{alg:DISPL} outperforms a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). We also show that image regions have to be adaptively defined on the image content, and that operating on a Voronoi partition of the scene in $K$ regions obtained by clustering $[r(x), c(x)]$ leads to performance loss (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).

>>>>

The proposed tampering-detection algorithm analyzes a sequence of frames $\{z_t, t=1,\dots\}$ to detect the time instant $\tau^*$ when tampering like \eqref{eq:model_defocus} or \eqref{eq:model_displacement} occurs. We assume that $T_0$ tampering-free frames are provided for training.

@@

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consist in computing the indicators, in particular $g$. Computing $g$ requires, when using the Sobel filters in~\eqref{eq:normaGradiente}, $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}, while computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively. Detecting outliers in the indicators requires two comparisons per frame: thus, monitoring regions instead of the whole image has a negligible impact on the overall computational complexity. Algorithm~\ref{alg:DISPL} has very low memory requirements: $l$ and $g$ indicators can be computed online, while $d$ requires to store a single frame in memory. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of separately monitoring regions in a tampering-detection framework like Algorithm~\ref{alg:DISPL}. To this purpose, we show that Algorithm~\ref{alg:DISPL} outperforms a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). We also show that image regions have to be adaptively defined on the image content, and that operating on a Voronoi partition of the scene in $K$ regions obtained by clustering $[r(x), c(x)]$ leads to performance loss (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).
